On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-29 docs/mvfits_paper/mvf.tex
fixing regelate
clarifying method for ansatz development re sigmas

In this, it may be that shown that $n$ may be entirely regelated to $\hat{P}$.

@@

\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for \textit{all} $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.

>>>>

In this, it may be that shown that $n$ may be entirely relegated to $\hat{P}$.

@@

\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for {individual} $\sigma_{\LMlmn}$, and then from these ansatz develop a single ansatz for all $\sigma_{\LMlmn}$.
